Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Atmosphere from Space \tnoteref{tnote1}

### 2021-12-01 paper/methodology.tex
Last commit in linux
- Update methodology section in paper
- Correct issues in TEC detrender

%We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible. A list of the stations where we got RINEX data is available in table \ref{tab:table-stations}. Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.

@@

%  The obtained RINEX files are compressed in Hatanaka format, developed at the Geographical Survey Institute by Y. Hatanaka \citep{Kumar:2012}. From this files we may estimate the Slant Total Electron Content (sTEC) and the Vertical Total Electron Content (vTEC) which may be computed in the following way:

@@

  Both parameters sTEC and vTEC are computed using a software developed by Gopi K. Seemala, publicly available at \url{https://seemala.blogspot.com/}.

>>>>

We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible. A list of the stations where we got RINEX data is available in table%\ref{tab:table-stations}
. Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.

@@

  The obtained RINEX files are compressed in Hatanaka format, developed at the Geographical Survey Institute by Y. Hatanaka \citep{Kumar:2012}. From this files we may estimate the Slant Total Electron Content (sTEC) and the Vertical Total Electron Content (vTEC) which may be computed in the following way:

@@

  % Both parameters sTEC and vTEC are computed
 Using a software developed by Gopi K. Seemala, publicly available at \url{https://seemala.blogspot.com/}, we computed the slant TEC (TEC) and vertical TEC (vTEC) for a several number of GPS satellites, each one identified with a PseudoRandom Noise code (PRN). For each station, we filtered all the PRN and data that lie in a window of 30 minutes around the time the event was reported. Then we estimated the signal trend using a Savitsky-Golay filter and substracting the original signal from the trend.

  \subsection{Wavelet analysis}
